Optimal forward modeling of gravitational fields using tesseroids with adaptive discretization

### 2014-09-02 body.tex
Cite eq when checking the distance-size condition

However, this would result in unnecessary divisions,
specially if one dimension of the tesseroid is much smaller than the others.
A more efficient approach is to check if the condition is met for each of the
three dimensions of the tesseroid ($L_r$, $L_\phi$, and $L_\lambda$).
We only divide the tesseroid in half along dimensions for which the condition
is not met.

>>>>

However, this would result in unnecessary divisions,
specially if one dimension of the tesseroid is much smaller than the others.
A more efficient approach is
to check if equation~\ref{eq:ratio} is met
for each of the three dimensions of the tesseroid
($L_r$, $L_\phi$, and $L_\lambda$).
We only divide the tesseroid in half
along dimensions for which the condition is not met.
